|

### 2020-11-25 01-Chp1-Introduction.Rmd
This time for sure

This is a test of the bibliography (@Darwin1859)

>>>>

## Aims and Objectives of the thesis

### Aim

```{r}
f <- flextable::flextable(robvis::data_rob2)

f <- flextable::autofit(f)

f
```

### Objective

## Chapter Overview

* __Chapter \@ref(background-heading):__ Background information on dementia and blood lipid levels. This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis. 
* __Chapter \@ref(sys-rev-tools-heading)__ This Chapter introduces new evidence synthesis two tools built in R: `robvis` and `medrixvr`. The motivation for, development and impact of, and future plans for these tools are outlined.
* __Chapter \@ref(sys-rev-heading)__ This Chapter describes the
* __Chapter \@ref(cprd-analysis):__ This Chapter examines the relationship between lipid-regaulting agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England. 
* __Chapter \@ref():__ This Chapter seeks

## Thesis Output

The outputs of this thesis are detailed below, and include published peer review papers, presentations at conferences, open source evidence synthesis tools, and . . .

### Peer reviewed papers

__Include other papers I have been involved in?__

### Papers under review

* McGuinness et al.

### Software

* `robvis`: An R package and associated `shiny` web application that allows users to easily visualise the results of risk of bias graphs.

* `medrxvir`: An R package and associated `shiny` web application that allows users to easily search and retrieve bibliographic data from the medRxiv^[https://www.medrxiv.org/] preprint repository.

### Talks

* Talk at Cochrane on medrxivr
* Webinar to Evidence Synthesis Ireland on Risk of Bias test

## Summary

*
* 
*

### 2020-11-25 03-Chp2-Systematic-Review.Rmd
This time for sure

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

@@

```{r, echo = FALSE}
knitr::read_chunk("scripts/Chp2-Systematic-Review.R")
```

@@

#### Exclusion
Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded. Studies which present no evidence of attempting to exclude prevalent cases from their analyses will also be excluded. Studies that measure change in continuous cognitive measures (e.g. MoCA score) without attempt to map these scores to ordinal groups (e.g. no dementia/MCI/dementia) will be excluded. Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study’s status. Studies that are reported in insufficient detail (e.g. only in conference abstracts, new, letters, editorials and opinion) will be excluded. Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles. Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a “multidomain intervention” where the lipid-regulating agent is included in each arms (e.g. for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) will be excluded.

@@

@@

```{r prisma-flow, echo = FALSE, warning=FALSE}
```

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2:  
      toc: false
      toc_depth: 3
      reference_docx: word-styles-reference-01.docx
  bookdown::html_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

@@

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
knitr::read_chunk("R/Chp2-Systematic-Review.R")
```

@@

#### Exclusion
Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded. Studies which present no evidence of attempting to exclude prevalent cases from their analyses will also be excluded. Studies that measure change in continuous cognitive measures (e.g. MoCA score) without attempt to map these scores to ordinal groups (e.g. no dementia/MCI/dementia) will be excluded. Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study’s status. Studies that are reported in insufficient detail (e.g. only in conference abstracts, new, letters, editorials and opinion) will be excluded. Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles. Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a “multi-domain intervention” where the lipid-regulating agent is included in each arms (e.g. for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) will be excluded.

Excluded studies performing autopsy unless it was done under accepted criteria
Exclude studies using a dietary intervention, for example omega-3 fatty acid enriched diet, as it hard to disentangle the effect of other elements contained within te diet, vs simple tablet based supplements of

@@

Harmonisation of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorising lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.

@@

### Screening results

#### Inter-rater reliability

Inter- and intra-rater reliability was asssessed for a 10% subsample of records at the title and abstract screening stage. Intra-rater reliability involved a sinlge reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliabilty was chosen over other methods of assessing inter-rater reliability such as percent agreeement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does. [@cohen1960: [@gwet2008; @wongpakaran2013]

How to interpret agreement co-efficients is widely debated. Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:kappa-table).

Gwet's AC1 is calculated using the following:

-> Insert formula here. Need to be sure of how to calculate. [@gwet2008; @sim2005]

```{r gwet-table, echo = FALSE}
```

```{r agreement-table-inter, echo = FALSE}
```

```{r agreement-table-intra, echo = FALSE}
```

For the inter-rater reliability, percentage agreement was 97.3% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)), while for the intra-rater reliability, agreement was 98.6% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)).

The discrepancy between the percent agreement and the associated value of AC is expected, due to the heavy imbalance in this sample towards exclusion.[@feinstein1990]

Those records which were excluded in the inital screening , but were included either by the same reviewer on their second vieweing (n=4), or by the second reviewer (n=29), were investigated. This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline vs mild cognitive impairment and the definition of eligible lipids.

#### PRISMA flowchart

```{r prisma-flow, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="PRISMA flow diagram, detailing the movement of studies through the systematic review."}
```

Following deduplication, the titles and abstracts of 16109 records were assessed for eligibility. 387 were deemed potentially eligible and the full text records for these were requested and screened.

A breakdown of records by

## Included studies

XXXX studies met the criteria for inclusion in the review

####

### 2020-11-25 04-Ch3-CPRD-Analysis.Rmd
This time for sure

# Chapter 3: Primary analysis of lipid regulating agents and dementia
\minitoc <!-- this will include a mini table of contents-->

@@

@@

Potential biases included time varying confounding, selection bias due to censoring on death and 
We performed a Cox

>>>>

# Primary analysis of lipid regulating agents and dementia {#cprd-analysis}
\minitoc <!-- this will include a mini table of contents-->

@@

Might be able to get around this by pointing

@@

Potential biases included time varying confounding, selection bias due to censoring on death and 
We performed a Cox  test this si to addd some words.

### 2020-11-25 front-and-back-matter/_acknowledgements.Rmd
This time for sure

This is where you will normally thank your advisor, colleagues, family and friends, as well as funding and institutional support. In our case, we will give our praises to the people who developed the ideas and tools that allow us to push open science a little step forward by writing plain-text, transparent, and reproducible theses in R Markdown.

\begin{flushright}
Luke McGuinness \\
Canynge Hall, Bristol \\
1 December 2021
\end{flushright}

>>>>

Additionally, I would like to thank Sharen O’Keefe.

\begin{flushright}
Canynge Hall, Bristol \\
1 December 2021
\end{flushright}

### 2020-11-25 index.Rmd
Major changes
This time for sure

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy in Population Health Sciences
degreedate: TBC
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.Rmd"), collapse = '\n  ')`
dedication: For Brendan McHugh
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations

@@

#####################
## PDF formatting  ##
#####################
abstractseparate: true  # include front page w/ abstract for examination schools?
bib-humanities: true   #set to true if you want in-text references formatted as author-year
doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
draft: true # add as DRAFT mark in the footer?
page-layout: nobind #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print
toc-depth: 2 # depth of heading to include in table of contents
lof: true # list of figures in front matter?
lot: true # list of tables in front matter?
mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
mini-lot: false  # mini-list of tables by start of each chapter?
mini-lof: false  # mini-list of figures by start of each chapter?

@@

#####################
## output options  ##
#####################
output:
  bookdown::pdf_book:
    template: templates/template.tex
    keep_tex: true
    citation_package: none  
    pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections
  bookdown::gitbook:
    css: templates/style.css
    download: ["pdf"]
    split_bib: false
    config:
      toc:
        before: |
          <li><a href="./">Thesis - Draft</a></li>
        after: |
          <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>

      sharing:
        facebook: false
        twitter: yes
        all: false
  bookdown::word_document2:
    toc: true   
link-citations: true
documentclass: book

@@

```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
source('scripts_and_filters/create_chunk_options.R')
```
<!--
Include the create_chunk_options chunk above at the top of your index.Rmd file
This will include code to create additional chunk options (e.g. for adding author references to savequotes)
If you need to create your own additional chunk options, edit the file scripts/create_chunk_options.R
-->

```{r introduction, child = '_00-introduction.Rmd'}
```

>>>>

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy in Population Health Sciences
degreedate: TBC
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.Rmd"), collapse = '\n  ')`
declaration: |
  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
dedication: For Brendan McHugh
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations

@@

#####################
## PDF formatting  ##
#####################
abstractseparate: true  # include front page w/ abstract for examination schools?
bib-humanities: false   #set to true if you want in-text references formatted as author-year
doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
draft: false # add as DRAFT mark in the footer?
page-layout: nobind #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print
toc-depth: 2 # depth of heading to include in table of contents
lof: true # list of figures in front matter?
lot: true # list of tables in front matter?
mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
mini-lot: false  # mini-list of tables by start of each chapter?
mini-lof: false  # mini-list of figures by start of each chapter?

@@

#####################
## output options  ##
#####################
output:
  bookdown::pdf_book:
    template: templates/template.tex
    keep_tex: true
    citation_package: none 
    pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections
  bookdown::gitbook:
    css: templates/style.css
    download: ["pdf"]
    output_dir: "docs"
    split_bib: false
    config:
      toc:
        before: |
          <li><a href="./">Thesis - Draft</a></li>
        after: |
          <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
      sharing:
        facebook: false
        twitter: yes
        all: false
  bookdown::word_document2:
    output_dir: "docs"
    toc: true
    toc_depth: 2
    reference_docx: templates/word-styles-reference-01.docx   
link-citations: true
documentclass: book

@@

```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
source('scripts_and_filters/create_chunk_options.R')
```
<!--
Include the create_chunk_options chunk above at the top of your index.Rmd file
This will include code to create additional chunk options (e.g. for adding author references to savequotes)
If you need to create your own additional chunk options, edit the file R/create_chunk_options.R
-->

```{r introduction, child = 'front-and-back-matter/_00-introduction.Rmd'}
```
